Eleven years of student replication projects provide evidence on the correlates of replicability in psychology

### 2023-10-16 code/process.Rmd
found p-value error in parse stats
if tval or whatever was negative, pval was in wrong range since it
takes the upper portion and then x2
now fixed with abs()
rerun models; add closeness and pre-reg stuff to ms

raw <- readxl::read_xlsx(here("data","raw_data.xlsx"), 
                       sheet="aligned data", skip=1) |> select(target_lastauthor_year, sensitivity, include,
         status, status_explanation,  academic_year, journal, target_cite, article_link, study_number,  subfield, target_year, stanford_internal, 
         open_data, open_materials, target_on_turk, replication_on_turk, 
         within_between, single_vignette, repeated_measure,
         target_N, target_raw_stat, effect_description, same_dir, replication_N,
         replication_raw_stat, replicated_instructor_code, replicated_report_code,
         adjudicated_replication_code) |> write_csv(here("data","raw_data.csv"))
```

@@

```{r}
d <- read_csv(here("data", "raw_data.csv")) |> 
  select(target_lastauthor_year, sensitivity, include,
         status, academic_year, subfield, target_year, stanford_internal, 
         open_data, open_materials, target_on_turk, replication_on_turk, 
         within_between, single_vignette, repeated_measure,
         target_N, target_raw_stat, same_dir, replication_N,
         replication_raw_stat, replicated_instructor_code, replicated_report_code,
         adjudicated_replication_code)

@@

# Parsing

@@

>>>>

raw <- readxl::read_xlsx(here("data","raw_data.xlsx"), sheet="aligned data", skip=1) |> 
  mutate(student_name_shared=ifelse(is.na(student_name_shared), "N/A", student_name_shared),
         replication_report_included=ifelse(is.na(replication_report_included), "no", replication_report_included)) |> 
  select(target_lastauthor_year, student_name_shared, replication_report_included, how_close, sensitivity, include,
         status, status_explanation,  academic_year, journal, target_cite, article_link, study_number,  subfield, target_year, stanford_internal, 
         open_data, open_materials, target_on_turk, replication_on_turk, 
         within_between, single_vignette, repeated_measure,
         target_N, target_raw_stat, effect_description, same_dir, replication_N,
         replication_raw_stat, replicated_instructor_code, replicated_report_code,
         adjudicated_replication_code) |> write_csv(here("data","raw_data.csv"))
```

@@

```{r}
d <- read_csv(here("data", "raw_data.csv")) |> 
  select(target_lastauthor_year, sensitivity, include, how_close,
         status, academic_year, subfield, target_year, stanford_internal, 
         open_data, open_materials, target_on_turk, replication_on_turk, 
         within_between, single_vignette, repeated_measure,
         target_N, target_raw_stat, same_dir, replication_N,
         replication_raw_stat, replicated_instructor_code, replicated_report_code,
         adjudicated_replication_code)

@@

# Closeness

```{r}
 d |> filter(include %in% c("exp","pred_int", "stats")) |> group_by(how_close) |> tally()

```
# Parsing

@@

```{r}
#found error in pval calculation related to sign flips

test %>% ungroup() %>% summarize(target=quantile(target_p_calc, na.rm=T), rep=quantile(rep_p_calc, na.rm=T))
```

### 2023-10-16 paper/coverletter/rsos_response.tex
rerun models; add closeness and pre-reg stuff to ms

\documentclass{stanfordletter}
%\makelabels
\usepackage{todonotes}
\usepackage{varioref}
\usepackage{xr}
%\externaldocument[paper-]{../revision}
\usepackage[american]{babel}
\usepackage{csquotes}
\usepackage[backend=biber,style=apa,doi=false,url=false,hyperref=true,apamaxprtauth=30,uniquename=false]{biblatex}
\DeclareLanguageMapping{american}{american-apa}
%\bibliography{../draft0}
\newcommand{\citet}[1]{\textcite{#1}}
\newcommand{\citep}[1]{\parencite{#1}}

%\makelabels
\newcommand{\theysaid}[1]{\begin{leftbar} \noindent 
		\textsl{ #1}\end{leftbar}}
\newcommand{\revised}[1]{\begin{quote}		#1 \end{quote}}

\begin{document}
	\name{Veronica Boyce}
	\signature{Veronica Boyce \\ Maya Mathur \\ Michael C. Frank}

@@

          \theysaid{Reviewer comments to Author:

          Reviewer: 1
          Comments to the Author(s)
          I have read this manuscript with great enthusiasm. It provides an important infusion of new data into a field that is very much oversaturated with analyses of what little data there is.
        }

        \theysaid{

          I find the report to be clearly written, well-documented, of a sensible length, and appropriately cautious when discussing the generalizability and potential causal implications of the reported results. But for a single minor issue, I believe the report could be accepted as is.

          The only thing I miss in the current manuscript is some description/discussion of how close/conceptual replications in the sample tended to be. See LeBel et. al. (2018, figure 1; https://doi.org/10.1177/2515245918787489) for a taxonomy of replication closeness. It would not need to be a long section, and I am not saying the authors need to code closeness for all studies included, or anything like that. However, I recommend adding a short paragraph to give readers a sense of how closely the original procedures were followed in the replications (on average/in general). The rationale being that I would generally expect a higher replication rate the closer replication procedures are to the original. Having a sense of what mix of close/conceptual replications in this sample is thus relevant for my interpretation of the overall replicability estimate.}

@@

@@

@@

@@

          	\theysaid{
          	Minor typos:
          	section 2.1 "of replications has outcomes with" should be "had"
          	section 4.3 "ramapped" should be "remapped"
          }
          Fixed, thank you!

>>>>

\documentclass{stanfordletter}
\makelabels
\usepackage{todonotes}
\usepackage{varioref}
\usepackage{xr}
\externaldocument[paper-]{../revision}
\usepackage[american]{babel}
\usepackage{csquotes}
\usepackage[backend=biber,style=apa,doi=false,url=false,hyperref=true,apamaxprtauth=30,uniquename=false]{biblatex}
\usepackage{framed}
\DeclareLanguageMapping{american}{american-apa}
%\bibliography{../draft0}
\newcommand{\citet}[1]{\textcite{#1}}
\newcommand{\citep}[1]{\parencite{#1}}

\makelabels
\newcommand{\theysaid}[1]{\begin{leftbar} \noindent 
		\textsl{ #1}\end{leftbar}}
\newcommand{\revised}[1]{\begin{quote}		#1 \end{quote}}

\usepackage{longtable,booktabs,array}
\usepackage{float}
\begin{document}
	\name{Veronica Boyce}
	\signature{Veronica Boyce \\ Maya Mathur \\ Michael C. Frank}

@@

          \theysaid{Reviewer comments to Author:\\
          Reviewer: 1 \\
          Comments to the Author(s)}

          \theysaid{I have read this manuscript with great enthusiasm. It provides an important infusion of new data into a field that is very much oversaturated with analyses of what little data there is.}

        \theysaid{I find the report to be clearly written, well-documented, of a sensible length, and appropriately cautious when discussing the generalizability and potential causal implications of the reported results. But for a single minor issue, I believe the report could be accepted as is.}

          \theysaid{The only thing I miss in the current manuscript is some description/discussion of how close/conceptual replications in the sample tended to be. See LeBel et. al. (2018, figure 1; https://doi.org/10.1177/2515245918787489) for a taxonomy of replication closeness. It would not need to be a long section, and I am not saying the authors need to code closeness for all studies included, or anything like that. However, I recommend adding a short paragraph to give readers a sense of how closely the original procedures were followed in the replications (on average/in general). The rationale being that I would generally expect a higher replication rate the closer replication procedures are to the original. Having a sense of what mix of close/conceptual replications in this sample is thus relevant for my interpretation of the overall replicability estimate.
          }

@@

          can't always tell if close or very close b/c had to guess based on whether materials were open and whether student mentioned having received from authors.

		student reports has a "differences" section -- this combined with platform and open materials and if they mentioned getting materials from authors.

		not quite sure how to code in some cases

@@

          coded based on what is being analyzed -- sometimes there were additional measures in original or this is the behavioral portion of an fmri etc

          assuming that switching from college to crowdsourced is not a difference in sample 
          and that reducing number of trials (ex. in trade-off with number of participants) doesn't prevent "close

@@

          Coauthors: In prior collaborations with students, we have invited students prospectively to be co-authors (Hawkins et al., 2018; Hardwicke et al., 2018). In those projects, we gave opportunities to engage with the research design throughout the process as well as approval over the manuscript. In this case, our study was based on retrospective coding of a large sample of projects. We had no assurance that we could contact all students for input (and had we been able to reach them, they might not have been interested). Further, we did not see ways that we could engage them with the research design prospectively to provide meaningful opportunities for contribution. Instead, we viewed this study as an archival investigation of course records - a meta-analysis of gray literature. (Note that we did attempt to contact all students to alert them to the project and provide them with an opportunity to include their course project in the shared materials).

@@

          But, for your edification, we did run the descriptive summary and the bivariate correlates on the Psych Science subsample.

          We were unable to use journal as a predictor in the models because of very uneven representation across journals. By far the most represented journal was Psychological Science, with 80 original papers. Other journals had at most a few papers in the sample.

          Here we present bivariate analyses on the subset of the data coming from Psych Science. This is a post-hoc split of the data.

          Overall, this split looks similar to the overall sample. Of note, publication year is correlated with replication success in this sample, but is not substantially correlated overall.

\begin{center}

          Descriptive properties of the Psych Science portion of the replication dataset. For categorical features, counts and percentages are given. For continuous features, the median value and interquartile range are given.

          \fontsize{10}{12}\selectfont
          \begin{tabular}[t]{lc}
          	\toprule
          	Feature & Summary\\
          	\midrule
          	Subfield & \\
          	\hspace{1em}Cognitive & 23 (29\%)\\
          	\hspace{1em}Social & 39 (49\%)\\
          	\hspace{1em}Other psych & 15 (19\%)\\
          	\hspace{1em}Non-psych & 3 (3.8\%)\\
          	Open data & 35 (44\%)\\
          	Open materials & 50 (63\%)\\
          	Switch from in-person to online & 33 (41\%)\\
          	Original authors at Stanford & 6 (7.5\%)\\
          	Within subjects design & 36 (45\%)\\
          	Single vignette & 41 (51\%)\\
          	Number of trials & 4 (1, 59)\\
          	Publication Year & 2016 (2014, 2017)\\
          	Original sample size & 97 (48, 155)\\
          	Replication sample size & 61 (30, 125)\\
          	Ratio of replication/original sample sizes & 0.79 (0.47, 1.05)\\
          	Original effect size (SMD) & 0.61 (0.47, 0.99)\\
          	Original p-value & 0.0003 (0.0000, 0.0070)\\
          	\bottomrule
          \end{tabular}

     The unadjusted Pearson correlations between each individual predictor and the subjective replication score for the Psych Science subsample.

          \fontsize{10}{12}\selectfont
          \begin{tabular}[t]{ccl}
          	\toprule
          	r & p & Predictors\\
          	\midrule
          	0.397 & 0.000 & Within participants design (versus between participants)\\
          	0.297 & 0.007 & Publication year\\
          	0.288 & 0.010 & Open data\\
          	0.214 & 0.057 & Non psychology (versus cognitive psych)\\
          	0.171 & 0.130 & Log number of  trials\\
          	0.167 & 0.139 & Other psychology (versus cognitive psych)\\
          	0.030 & 0.790 & Open materials\\
          	-0.052 & 0.644 & Log original sample size\\
          	-0.114 & 0.315 & Log ratio between replication and original sample sizes\\
          	-0.163 & 0.149 & Stanford affiliation of original authors at time of replication\\
          	-0.255 & 0.022 & Switch to online for replication (versus same modality for original and replication)\\
          	-0.268 & 0.016 & Social psychology (versus cognitive psych)\\
          	-0.311 & 0.005 & Single vignette (versus multiple items/inductions per condition)\\
          	\bottomrule
          \end{tabular}
          \end{center}

Notably, the Psych Science subsample is pretty similar descriptively to the overall sample. The biggest difference in the bi-variate correlations is the Publication Year is correlated with replication success in the Psych Science portion, but not the overall sample (possible due to more limited time frame for Psych Science, and substantial changes in how the journal was run during that time frame). 
          	\theysaid{
          	Minor typos:\\
          	section 2.1 "of replications has outcomes with" should be "had"\\
          	section 4.3 "ramapped" should be "remapped"
          }
          Fixed, thank you!

### 2023-10-16 paper/manuscript.Rmd
rerun models; add closeness and pre-reg stuff to ms

```{r, include=F}
matching <- d |> filter(include!="unusable") |> mutate(match=ifelse(replicated_instructor_code==replicated_report_code,1,0)) |> group_by(match) |> tally()

d |> filter(include!="unusable")
irr <- cor.test(d$replicated_instructor_code, d$replicated_report_code, method="spearman")$estimate
pred_int_avail <- d |> filter(include %in% c("stats", "pred_int")) |> tally()

@@

These replications were all conducted on short time scales, within a constrained class budget. In some cases the budget limited the number of participants who could be recruited, occasionally below what the original study included or what power analyses suggested. The replications had a median post-exclusion sample size that was `r round(ratio_dist[3]*100)`% of the original sample size.  In nearly all cases, replications were conducted online, with recruitment from Amazon Mechanical Turk (the default from 2011 to 2020) or Prolific (the default from 2021 -- 2022).

@@

desc <- d %>% mutate(target_d_calc=ifelse(include=="stats", target_d_calc, NA),
             target_p_calc=ifelse(include=="stats",target_p_calc, NA),
      switch_modality=ifelse(target_on_turk!=replication_on_turk,1,0),
         ss_ratio=replication_N/target_N)%>% 
  select("subfield","open_data", "open_materials","switch_modality",  "stanford_internal","within_between","single_vignette","repeated_measure","target_year","target_N","replication_N", "ss_ratio", "target_d_calc", "target_p_calc") %>% 
  mutate(subfield=factor(subfield, levels=c("cognitive", "social", "other-psych", "non-psych"), labels=c("Cognitive", "Social", "Other psych", "Non-psych")),
         within_between=ifelse(within_between=="between", 0, 1)) %>% 
             tbl_summary(
               label=list(
                 subfield ~ "Subfield",
                 stanford_internal ~ "Original authors at Stanford",
                 target_year~ "Publication Year",
                 single_vignette ~ "Single vignette",
                 open_data ~ "Open data",
                 open_materials ~ "Open materials",
                 within_between ~ "Within subjects design",
                 repeated_measure ~ "Number of trials",
                 target_N ~ "Original sample size",
                 replication_N ~ "Replication sample size",
                 ss_ratio ~ "Ratio of replication/original sample sizes",
                 target_d_calc ~"Original effect size (SMD)",
                 target_p_calc ~ "Original p-value",
                 switch_modality ~ "Switch from in-person to online"
               ),
               statistic = list(all_continuous() ~ "{mean} ({sd})", all_continuous() ~ "{median} ({p25}, {p75})"),
               digits=list(target_year ~ 0, target_p_calc ~4),
    missing="no",
             ) %>% modify_header(label="Feature", stat_0="Summary") %>% 
    modify_footnote(update = everything() ~ NA)

@@

```{r corr-plot, out.height="40%", fig.width=8, fig.height=4.5, fig.pos="ht", fig.cap="Correlations between predictors. See TODO Table 1 or Methods for descriptions. "}
dat <-  for_cor %>% mutate(cognitive=ifelse(subfield=="cognitive",1,0)) %>% select(-sub_rep, -subfield)

@@

@@

# reduce the size of correlation matrix
melted_corr_mat <-melt(corr_mat) %>% 
  mutate(value=ifelse(Var1==Var2, NA, value),
         value=ifelse(Var1 %in% c("cognitive", "non_psych", "other_psych", "social") &
                        Var2 %in% c("cognitive", "non_psych", "other_psych", "social"),
                      NA, value)) %>% 
  mutate(Var1=factor(Var1, levels=c("social", "cognitive", "other_psych", "non_psych", "is_within", "single_vignette", "stanford", "change_platform", "open_data", "open_mat", "pub_year", "log_trials", "log_sample", "log_ratio_ss"), labels=c("Social psych", "Cognitive psych", "Other psych", "Non-psych", "Within participants design", "Single vignette ","Stanford affiliated", "Switch to online", "Open data", "Open materials", "Publication year", "Log # of trials", "Log original sample size", "Log ratio rep/original sample sizes")),
         Var2=factor(Var2, levels=c("social", "cognitive", "other_psych", "non_psych", "is_within", "single_vignette", "stanford", "change_platform", "open_data", "open_mat", "pub_year", "log_trials", "log_sample", "log_ratio_ss"), labels=c("Social psych", "Cognitive psych", "Other psych", "Non-psych", "Within participants design", "Single vignette ","Stanford affiliated", "Switch to online", "Open data", "Open materials", "Publication year", "Log # of trials", "Log original sample size", "Log ratio rep/original sample sizes")))

# plotting the correlation heatmap
ggplot(data = melted_corr_mat, aes(x=Var1, y=Var2,
                                   fill=value)) + #scale_fill_viridis()+
  theme_classic()+
  scale_fill_gradient2(low="#763386",high="#FDE725FF", na.value="grey")+
  labs(x="", y="")+
  geom_tile(alpha=.7)+
  theme(axis.text.x = element_text(angle = 40, vjust = 1, hjust=1), legend.position="none")+
  geom_text(aes(label=value), size=3)

@@

Our results are limited by the sample of studies we included, which are limited in number and may not be representative of the studies of interest to psychologists as a whole. Further, our predictor variables were not manipulated, so they cannot be interpreted as causing (non-)replication, but only as correlational markers. Some of the correlates are most easily interpreted as being about the original study, and others reflect the closeness of the replication to the original. For instance, while within-participants designs are more likely to replicate than between-participants designs, this predictor could also be related to the types of experiments that tend to be run in each design. Given the strong relationship of this factor to replicability, slightly more skepticism and critical reading of between-participants designs may be warranted, but this correlation, by itself, does not mean scientists should prefer within-participants designs.

@@

# Methods
Our pre-registration, code, and coded data are available at https://osf.io/xwn9m/ [@osfdata]. <!--TODO VIEW ONLY https://osf.io/xwn9m/?view_only=ebb6df1ae97045cfa5154d6119ec20b1-->

@@

Four of the replication projects were included in RP:P, and 10 were previously reported in @hawkins2018 (which reported 11 student replications from the 2015-2016 class; one of those was excluded from the current sample for being non-experimental).

>>>>

```{r, include=F}
matching <- d |>  mutate(match=ifelse(replicated_instructor_code==replicated_report_code,1,0)) |> group_by(match) |> tally()

irr <- cor.test(d$replicated_instructor_code, d$replicated_report_code, method="spearman")$estimate
pred_int_avail <- d |> filter(include %in% c("stats", "pred_int")) |> tally()

@@

```{r}
closeness <- d |> group_by(how_close) |> tally() |> mutate(pct=(n/sum(n)*100) |> round())

These replications were all conducted on short time scales, within a constrained class budget. In some cases the budget limited the number of participants who could be recruited, occasionally below what the original study included or what power analyses suggested. The replications had a median post-exclusion sample size that was `r round(ratio_dist[3]*100)`% of the original sample size.  In nearly all cases, replications were conducted online, with recruitment from Amazon Mechanical Turk (the default from 2011 to 2020) or Prolific (the default from 2021 -- 2022). The goal was for replications to be as close as possible to the original, but budgetary constraints, inability to option original materials, and primarily using online samples meant that replications varied in their degree of closeness to the original. According to the schema from @lebel2018, `r pluck(closeness,3,2)`% of studies were exact replications, `r pluck(closeness,3,4)`% were very close replications, `r pluck(closeness,3,1)`% were close replications, and `r pluck(closeness,3,3)` were far replications (See Methods for more details on common deviations).

@@

desc <- d %>% mutate(target_d_calc=ifelse(include=="stats", target_d_calc, NA),
             target_p_calc=ifelse(include=="stats",target_p_calc, NA),
      switch_modality=ifelse(target_on_turk!=replication_on_turk,1,0),
         ss_ratio=replication_N/target_N)%>% 
  select("subfield","open_data", "open_materials","switch_modality",  "stanford_internal","within_between","single_vignette","repeated_measure","target_year","target_N","replication_N", "ss_ratio", "target_d_calc", "target_p_calc") %>% 
  mutate(subfield=factor(subfield, levels=c("cognitive", "social", "other-psych", "non-psych"), labels=c("Cognitive", "Social", "Other psych", "Non-psych")),
         within_between=ifelse(within_between=="between", 0, 1)) %>% 
             tbl_summary(
               label=list(
                 subfield ~ "Subfield",
                 stanford_internal ~ "Original authors at Stanford",
                 target_year~ "Publication Year",
                 single_vignette ~ "Single vignette",
                 open_data ~ "Open data",
                 open_materials ~ "Open materials",
                 within_between ~ "Within participants design",
                 repeated_measure ~ "Number of trials",
                 target_N ~ "Original sample size",
                 replication_N ~ "Replication sample size",
                 ss_ratio ~ "Ratio of replication/original sample sizes",
                 target_d_calc ~"Original effect size (SMD)",
                 target_p_calc ~ "Original p-value",
                 switch_modality ~ "Switch from in-person to online"
               ),
               statistic = list(all_continuous() ~ "{mean} ({sd})", all_continuous() ~ "{median} ({p25}, {p75})"),
               digits=list(target_year ~ 0, target_p_calc ~4),
    missing="no",
             ) %>% modify_header(label="Feature", stat_0="Summary") %>% 
    modify_footnote(update = everything() ~ NA)

@@

```{r corr-plot, out.height="40%", fig.width=8, fig.height=4.5, fig.pos="ht", fig.cap="Correlations between predictors. See TODO Table 1 or Methods for descriptions. "}
dat <-  for_cor %>% mutate(cognitive=ifelse(subfield=="cognitive",1,0)) %>% select(-sub_rep, -subfield) %>% select( "social", "cognitive", "other_psych", "non_psych","is_within", "single_vignette", "stanford", "change_platform", "open_data", "open_mat", "pub_year", "log_trials", "log_sample", "log_ratio_ss", )

@@

corr_mat[lower.tri(corr_mat)] <- NA

@@

# reduce the size of correlation matrix
melted_corr_mat <-melt(corr_mat) %>% 
  mutate(value=ifelse(Var1==Var2, NA, value),
         value=ifelse(Var1 %in% c("cognitive", "non_psych", "other_psych", "social") &
                        Var2 %in% c("cognitive", "non_psych", "other_psych", "social"),
                      NA, value)) %>% 
    filter(Var1!="log_ratio_ss") |> 
  mutate(Var1=factor(Var1, levels=c("social", "cognitive", "other_psych", "non_psych", "is_within", "single_vignette", "stanford", "change_platform", "open_data", "open_mat", "pub_year", "log_trials", "log_sample", "log_ratio_ss"), labels=c("Social psych", "Cognitive psych", "Other psych", "Non-psych", "Within participants design", "Single vignette ","Stanford affiliated", "Switch to online", "Open data", "Open materials", "Publication year", "Log # of trials", "Log original sample size", "Log ratio rep/original sample sizes"))) |> 
           filter(!Var2 %in% c("social", "cognitive","other_psych", "non_psych")) |> 
         mutate(Var2=factor(Var2, levels=c("social", "cognitive", "other_psych", "non_psych", "is_within", "single_vignette", "stanford", "change_platform", "open_data", "open_mat", "pub_year", "log_trials", "log_sample", "log_ratio_ss"), labels=c("Social psych", "Cognitive psych", "Other psych", "Non-psych", "Within participants design", "Single vignette ","Stanford affiliated", "Switch to online", "Open data", "Open materials", "Publication year", "Log # of trials", "Log original sample size", "Log ratio rep/original sample sizes")))

# plotting the correlation heatmap
ggplot(data = melted_corr_mat, aes(x=Var1, y=Var2,
                                   fill=value)) + #scale_fill_viridis()+
  theme_classic()+
      scale_y_discrete(limits=rev)+
  scale_fill_gradient2(low="#763386",high="#FDE725FF", na.value="grey")+
  labs(x="", y="")+
  geom_tile(alpha=.7)+
  theme(axis.text.x = element_text(angle = 40, vjust = 1, hjust=1), legend.position="none")+
  geom_text(aes(label=value), size=3)

@@

Our results are limited by the sample of studies we included, which are limited in number and may not be representative of the studies of interest to psychologists as a whole. Further, our predictor variables were not manipulated, so they cannot be interpreted as causing (non-)replication, but only as correlational markers. Some of the correlates are most easily interpreted as being about the original study, and others reflect the closeness of the replication to the original.

For instance, while within-participants designs are more likely to replicate than between-participants designs, this predictor could also be related to the types of experiments that tend to be run in each design. Additionally, as @greenwald1976 notes, within-participants designs can lead to practice effects, carry-over of treatments, and critically, sensitization effects, where participants reason about the contrast between conditions and respond differently due to that reasoning. Sensitization effects are a threat to internal validity, and could be replicable even in the absence of the effect itself being replicable.  Given the strong relationship of within-participants designs to replicability, slightly more skepticism and critical reading of between-participants designs may be warranted, but this correlation, by itself, does not mean scientists should prefer within-participants designs.

@@

# Methods
Our pre-registration, code, and coded data are available at https://osf.io/xwn9m/ [@osfdata].

At the onset of this project, all authors had some familiarity with the dataset. MCF taught PSYCH 254/251; MM and VB had each been students in the class. The coding of the data primarily took place before the pre-registration was finalized; the only way for us to know what variables were actually codeable and what forms of missingness were present in the data was to code it. Thus, the pre-registration was a pre-registration of the analyses and a "locking-in" of the coding scheme. VB coded both the predictor variables and was one of the coders of outcome variables, but these were coded in separate passes through the data.  <!--TODO VIEW ONLY https://osf.io/xwn9m/?view_only=ebb6df1ae97045cfa5154d6119ec20b1-->

## Deviations from pre-registration
The descriptive statistics and bivariate correlations between predictor and outcome variables were not pre-registered.

In the pre-registration, our research questions mentioned publication journal, but due to the distribution of journals, journal was not a predictor in the pre-registered model plan (or the actual models). Our pre-registration stated that we could not include students names or reports in the released dataset; we ended up letting students opt-in to associating their names with their projects and having their replication report included. Our pre-registration stated that any errors found would be noted; errors are noted in the data spreadsheet of the materials.

@@

Replications varied in how close they were to the original; while the goal was to replicate the original as closely as possible, some deviations were sometimes necessary. Student reports contained a section listing changes from the original. In response to a reviewer, we attempted to code studies using the classification scheme from @lebel2018.

Common reasons for replications being very close instead of exact were a switch from in-person to online and lack of access to the original instructions. (It was not always possible to tell if students had access to original wording and presentation style of materials.) Common reason for replications being only close included recreating materials when the original materials were not available and changing materials to fit the audience (ex. switching from UK to US English). (It was not always possible to determine if students had the original materials; in some cases students mentioned trying to obtain materials but did not indicate if they had succeeded.) Less common reasons for replications being only close included changing the number of trials per participant or reducing training periods.

Far replications were rare, but were primarily due to a couple deviations. In some cases an original study had a specific population (ex. high schoolers or hiring managers), and the replication was on a convenience population. The other main reason was changing the language of materials to English when cultural or linguistic factors were potentially relevant to the construct of interest.

Other common changes (that we did not consider as decreasing the closeness) were switching which convenience population was used (i.e. from college students to crowdworkers or from one crowdwork platform to another), changing or reducing demographic surveys (which were used only in exploratory or secondary analyses, if at all), and removing secondary measures that were not part of the analyses being replicated. 
Four of the replication projects were included in RP:P, and 10 were previously reported in @hawkins2018 (which reported 11 student replications from the 2015-2016 class; one of those was excluded from the current sample for being non-experimental).
